Reasoning About a Machine with Local Capabilities

### 2019-03-01 toplas/paper.tex
[TOPLAS] Make small textual improvements

\newcommand{\Rel}{\plaindom{Rel}}
\newcommand{\Rels}{\plaindom{Rels}}
\newcommand{\States}{\plaindom{WState}}
\newcommand{\RegionNames}{\plaindom{RegionName}}
\newcommand{\Regions}{\plaindom{Region}}
\newcommand{\Reg}{\plaindom{Reg}}
\newcommand{\Worlds}{\plaindom{World}}
\newcommand{\Wor}{\plaindom{Wor}}
\newcommand{\Worwk}{\Wor_{\futurewk}}
\newcommand{\Worstr}{\Wor_{\futurestr}}
\newcommand{\xiwk}{\xi_{\var{wk}}}
\newcommand{\xistr}{\xi_{\var{str}}}
\newcommand{\StorePred}{\plaindom{MemSegPred}}
\newcommand{\UPred}[1]{\plaindom{UPred}(#1)}
\newcommand{\DCPred}[1]{\plaindom{P}^\downarrow(#1)}

@@

\section{A Capability Machine with Local Capabilities}
\label{sec:capab-mach-with}
In this paper, we work with a formalization of a capability machine with all the characteristics of real capability machines as well as local capabilities much like CHERI's.
Otherwise, it is kept as simple as possible.
It is inspired by both the M-Machine~\citep{Carter:1994:HSF:195473.195579} and CHERI~\citep{Watson2015Cheri}.
To avoid tedious details irrelevant to the focus of this paper, we assume an
infinite address space and unbounded integers (see
\sectionname~\ref{sec:discussion} for more on this).

@@

\begin{figure}[htb]
  \centering
  \begin{equation*}
    \Phi  \rightarrow
    \begin{cases}
      \sem{\decode(n)}(\Phi) & \arraycolsep=0pt
      \begin{array}[t]{l}
        \text{if $\memreg(\pcreg) = \stdcap$ and $\start \leq \addr \leq \addrend$}\\ 
        \text{\;\;and $\perm \in \{ \exec,\rwx, \rwlx \}$ and $\memheap(\addr) = n$ }
      \end{array}
\\
      \failed                                 & \text{otherwise}
    \end{cases}
  \end{equation*}
  \begin{align*}
    \stdUpdatePc{\Phi} &=
                         \begin{cases}
                           \updateReg{\pcreg}{\var{newPc}} & \arraycolsep=0pt
                           \begin{array}[t]{l}
                             \text{if $\memreg(\pcreg) = \stdcap$}\\
                             \text{\;\;and $\var{newPc} = ((\perm,\gl),\start,\addrend,\addr + 1)$}
                           \end{array}
\\
                             \failed & \text{otherwise}
                         \end{cases}
  \end{align*}
  \begin{tabular}{|c|p{3.4cm}|>{\raggedright\arraybackslash}p{7.3cm}|}
    \hline
    $i$&$\sem{i}(\Phi)$&Conditions\\
    \hline 
    $\fail$&$\failed$&\\
    \hline
    $\halt$&$(\halted,\memheap)$&\\
    \hline
    $\move{\refreg{r_1}}{r_2}$& $\stdUpdatePc{}(\updateReg{r_1}{w})$&$r_2 \in \Regs \Rightarrow w = \memreg(r_2)$ and $r_2 \in \ints \Rightarrow w = r_2$\\
    \hline
    $\load{\refreg{r_1}}{\refheap{r_2}}$&$\stdUpdatePc{\updateReg{r_1}{w}}$&$\memreg(r_2) = \stdcap{}$ and  $w = \memheap(\addr)$ and $\start \leq \addr \leq \addrend$ and $\perm \in \{ \rwx, \rwlx, \exec, \readwrite, \readwritel, \readonly \}$ \\
    \hline
    $\restricttwo{\refreg{r_1}}{r_2}$&$\stdUpdatePc{}(\updateReg{r_1}{w})$  & $\memreg(r_2) = \stdcap$ and $(\perm',g') = \decodePermPair{\memreg(r_2)}$
                                                                              and $(\perm',g') \sqsubseteq (\perm,g)$ and  $w =((\perm',g'),\start,\addrend,\addr)$\\
    \hline
    \itoplas{$\subseg{\refreg{r_1}}{r_2}{r_3}$} & \itoplas{$\stdUpdatePc{\updateReg{r_1}{\var{w}}}$} &  \itoplas{$\memreg(r_1) = \stdcap$ and for $i \in \{2,3\}$ $n_i = \memreg(\rv_i)$ and $n_2 \in \nats$ and $\start \leq n_2$ and $n_3 \leq \addrend$ where either $n_3 \in \nats$ or ($n_3=\inftyend$ and $\addrend = \infty$) and $\perm \neq \entry$ and $w = ((\perm,\gl),n_1,n_2,\addr)$}\\
    \hline
    $\jmp{\lv}$&$\updateReg{\pcreg}{\var{newPc}}$& if $\memreg(r) = ((\entry,\gl),\start,\addrend,\addr)$, then $\var{newPc} = ((\exec,\gl),\start,\addrend,\addr)$ otherwise $\var{newPc} = \memreg(r)$\\
    \hline
    \itoplas{$\lea{\refreg{r_1}}{r_2}$} & \itoplas{$\stdUpdatePc{\updateReg{r_1}{\var{c}}}$} &\itoplas{$\memreg(r_1) = \stdcap$ and $n = \memreg(r_2)$ and $n \in \ints $ and $\perm \neq \entry$ and $\var{c} = ((\perm,\gl),\start,\addrend,\addr + n)$} \\
    \hline
    $\geta{\refreg{r_1}}{\refreg{r_2}}$ & $\stdUpdatePc{\updateReg{r_1}{\addr}}$ &
                                                $\memreg(r_2) = ((\_,\_),\_,\_,\addr)$\\
    \hline
    $\store{\refheap{r_1}}{\refreg{r_2}}$&$\stdUpdatePc{\updateHeap{\addr}{\var{w}}}$&$\memreg(r_1) = \stdcap$ and $\perm \in \{ \rwx, \rwlx, \readwrite, \readwritel\}$  and $\start \leq \addr \leq \addrend$ and $\var{w} = \memreg(r_2)$
                                                                                       and if $\var{w} = ((\_,\local),\_,\_,\_)$, then $\perm \in \{\rwlx,\readwritel \}$\\
    \hline
    \multicolumn{3}{|c|}{$\cdots$}\\
    \hline
    \_&$\failed$&otherwise\\
    \hline
  \end{tabular}
  \caption{An excerpt from the operational semantics.}
  \label{fig:op-sem}
\end{figure}

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,5) rectangle (7.6,11.5);
        \capbrace{(4.6,5)}{(4.6,12)}{sp}
      \end{scope}
    \end{tikzpicture}
    \caption{The stack just before we return to the adversary. Our stack frame
      is the topmost, and we do not have access to the adversary stack frame.}
  \label{fig:illu-intro}
  \end{subfigure}
\begin{subfigure}{0.033\linewidth}
  % padding
  \phantom{a}
\end{subfigure}
  \begin{subfigure}[t]{0.3\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace{(4.6,2)}{(4.6,12)}{sp}
      \end{scope}
    \end{tikzpicture}
    \caption{The stack just after we returned to the adversary but did not take
      care to clear our local stack frame.}
  \label{fig:illu-priv-data}
  \end{subfigure}
\begin{subfigure}{0.033\linewidth}
  % padding
  \phantom{a}
\end{subfigure}
  \begin{subfigure}[t]{0.3\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace{(4.6,2)}{(4.6,12)}{sp}
      \end{scope}
    \end{tikzpicture}
    \caption{The stack just after we returned to the adversary, and we did take
      care to clear our local stack frame.}
  \label{fig:illu-clear-priv}
  \end{subfigure}
  \begin{subfigure}[t]{0.33\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,7) rectangle (7.6,11.5);
        \capbrace{(4.6,7)}{(4.6,13)}{sp}
      \end{scope}
    \end{tikzpicture}
  \caption{The stack after an adversary has called us, and we have called the adversary.}
  \label{fig:illu-call-adv}
\end{subfigure}
\begin{subfigure}[t]{0.02\linewidth}
  % padding
  \phantom{a}
\end{subfigure}
  \begin{subfigure}[t]{0.3\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace{(4.6,2)}{(4.6,13)}{sp}
      \end{scope}
    \end{tikzpicture}
  \caption{The stack after the adversary has returned to us, and we have
    returned from the first adversary call. At this point, the adversary has
    access to the local state from the nested adversary call.}
  \label{fig:illu-adv-data}
\end{subfigure}
\begin{subfigure}[t]{0.02\linewidth}
  % padding
  \phantom{a}
\end{subfigure}
  \begin{subfigure}[t]{0.3\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace{(4.6,2)}{(4.6,13)}{sp}
      \end{scope}
    \end{tikzpicture}
  \caption{The stack after the adversary has returned to us, and we have
    returned from the first adversary call after we took care to clear the
    unused part of the stack.}
  \label{fig:illu-clear-all}
  \end{subfigure}
  \caption{Depictions of the stack in relation to stack clearing.
    The greyed out areas are parts of the stack that are not accessible at the
    time.
    The sp capability is the stack pointer.}
  \label{fig:ret-adv2}
\end{figure}
\textbf{Invoking the adversary} A slightly more complex case is invoking the
adversary. As above, we clear all the non-argument registers, as well as the
part of the stack that we are not using (because, as above, it may contain local
capabilities from previously executed code that the adversary could exploit in
the same way). We leave a copy of the stack pointer in $r_\stk$, but only after
we have used the $\subseg{}{}{}$ instruction to shrink its authority to the part
that we are not using ourselves.

@@

For technical reasons, we do not actually remove a revoked temporary region from the world, but we turn it into a special revoked region that exists for this purpose.
Such a revoked region contains no state transition system and puts no requirements on the memory.
It simply serves as a mask for a revoked temporary region.
Masking a region like this goes back to earlier work of \citet{Ahmed2004semantics} and was also used by \citet{Thamsborg:2011:KLR:2034773.2034831}.

@@

\begin{toplas}
  In order to be able to solve the recursive domain equation, we want the future world relations to be extensional.
  This means a future world cannot forget about region names in a past world.
  This is the reason we use masks rather than deleting the regions altogether.
  It does not, however, matter what kind of region is used as a mask; it is the region name we must retain.
  This is why we allow revoked regions to be replaced by other regions in the two future world relations.
  This may seem unnecessary as the future world relation allows new regions to be added. However, for technical reasons in private future worlds, we need to be able to reinstate old regions with the same region names as they had in a past world.
  Further, we do not want public future worlds to be able to prevent reinstation in private future worlds.
  Private future worlds cannot revoke permanent regions, so we cannot allow public future worlds to use permanent regions as masks for revoked regions.
\end{toplas}

@@

%subsection introduction
% \dominique{I would try to motivate the LR defs by saying that the LR is
%   constructed to express the FTLR and the FTLR says that if a piece of code only
%   has access to values respecting the invariants in a world, then it will
%   respect them itself too.} 
The logical relation defines semantically when values, program
counters, and configurations are capability safe. The logical relation is defined
found in \figurename{}s~\ref{fig:logrel} and~\ref{fig:perm-conds}, and
we provide some explanations in the following paragraphs. For space
reasons, we omit some definitions and explain them only verbally, but
precise definitions can be found in the appendix.

>>>>

\newcommand{\Rel}{\plaindom{Rel}}
\newcommand{\Rels}{\plaindom{Rels}}
\newcommand{\States}{\plaindom{RState}}
\newcommand{\RegionNames}{\plaindom{RegionName}}
\newcommand{\Regions}{\plaindom{Region}}
\newcommand{\Reg}{\plaindom{Reg}}
\newcommand{\Worlds}{\plaindom{World}}
\newcommand{\Wor}{\plaindom{Wor}}
\newcommand{\Worwk}{\Wor_{\futurewk}}
\newcommand{\Worstr}{\Wor_{\futurestr}}
\newcommand{\xiwk}{\xi_{\var{wk}}}
\newcommand{\xistr}{\xi_{\var{str}}}
\newcommand{\StorePred}{\plaindom{MemSegPred}}
\newcommand{\UPred}[1]{\plaindom{UPred}(#1)}
\newcommand{\DCPred}[1]{\plaindom{P}^\downarrow(#1)}

@@

\section{A Capability Machine with Local Capabilities}
\label{sec:capab-mach-with}
In this paper, we work with a formalization of a capability machine with all the characteristics of real capability machines as well as local capabilities much like CHERI's.
Otherwise, it is kept as simple as possible.
It is inspired by both the M-Machine~\citep{Carter:1994:HSF:195473.195579} and CHERI~\citep{Watson2015Cheri}.
To avoid tedious details irrelevant to the focus of this paper, we assume an
infinite address space and unbounded integers (see \sectionname~\ref{sec:discussion} for a discussion of these assumptions).

@@

\begin{figure}[htb]
  \centering
  \begin{equation*}
    \Phi  \rightarrow
    \begin{cases}
      \sem{\decode(n)}(\Phi) & \arraycolsep=0pt
      \begin{array}[t]{l}
        \text{if $\memreg(\pcreg) = \stdcap$ and $\start \leq \addr \leq \addrend$}\\ 
        \text{\;\;and $\perm \in \{ \exec,\rwx, \rwlx \}$ and $\memheap(\addr) = n$ }
      \end{array}
\\
      \failed                                 & \text{otherwise}
    \end{cases}
  \end{equation*}
  \begin{align*}
    \stdUpdatePc{\Phi} &=
                         \begin{cases}
                           \updateReg{\pcreg}{\var{newPc}} & \arraycolsep=0pt
                           \begin{array}[t]{l}
                             \text{if $\memreg(\pcreg) = \stdcap$}\\
                             \text{\;\;and $\var{newPc} = ((\perm,\gl),\start,\addrend,\addr + 1)$}
                           \end{array}
\\
                             \failed & \text{otherwise}
                         \end{cases}
  \end{align*}
  \begin{tabular}{|c|p{3.4cm}|>{\raggedright\arraybackslash}p{7.3cm}|}
    \hline
    $i$&$\sem{i}(\Phi)$&Conditions\\
    \hline 
    $\fail$&$\failed$&\\
    \hline
    $\halt$&$(\halted,\memheap)$&\\
    \hline
    $\move{\refreg{r_1}}{r_2}$& $\stdUpdatePc{}(\updateReg{r_1}{w})$&$r_2 \in \Regs \Rightarrow w = \memreg(r_2)$ and $r_2 \in \ints \Rightarrow w = r_2$\\
    \hline
    $\load{\refreg{r_1}}{\refheap{r_2}}$&$\stdUpdatePc{\updateReg{r_1}{w}}$&$\memreg(r_2) = \stdcap{}$ and  $w = \memheap(\addr)$ and $\start \leq \addr \leq \addrend$ and $\perm \in \{ \rwx, \rwlx, \exec, \readwrite, \readwritel, \readonly \}$ \\
    \hline
    $\restricttwo{\refreg{r_1}}{r_2}$&$\stdUpdatePc{}(\updateReg{r_1}{w})$  & $\memreg(r_2) = \stdcap$ and $(\perm',g') = \decodePermPair{\memreg(r_2)}$
                                                                              and $(\perm',g') \sqsubseteq (\perm,g)$ and  $w =((\perm',g'),\start,\addrend,\addr)$\\
    \hline
    \itoplas{$\subseg{\refreg{r_1}}{r_2}{r_3}$} & \itoplas{$\stdUpdatePc{\updateReg{r_1}{\var{w}}}$} &  \itoplas{$\memreg(r_1) = \stdcap$ and for $i \in \{2,3\}$ $n_i = \memreg(\rv_i)$ and $n_2 \in \nats$ and $\start \leq n_2$ and $n_3 \leq \addrend$ where either $n_3 \in \nats$ or ($n_3=\inftyend$ and $\addrend = \infty$) and $\perm \neq \entry$ and $w = ((\perm,\gl),n_2,n_3,\addr)$}\\
    \hline
    $\jmp{\lv}$&$\updateReg{\pcreg}{\var{newPc}}$& if $\memreg(r) = ((\entry,\gl),\start,\addrend,\addr)$, then $\var{newPc} = ((\exec,\gl),\start,\addrend,\addr)$ otherwise $\var{newPc} = \memreg(r)$\\
    \hline
    \itoplas{$\lea{\refreg{r_1}}{r_2}$} & \itoplas{$\stdUpdatePc{\updateReg{r_1}{\var{c}}}$} &\itoplas{$\memreg(r_1) = \stdcap$ and $n = \memreg(r_2)$ and $n \in \ints $ and $\perm \neq \entry$ and $\var{c} = ((\perm,\gl),\start,\addrend,\addr + n)$} \\
    \hline
    $\geta{\refreg{r_1}}{\refreg{r_2}}$ & $\stdUpdatePc{\updateReg{r_1}{\addr}}$ &
                                                $\memreg(r_2) = ((\_,\_),\_,\_,\addr)$\\
    \hline
    $\store{\refheap{r_1}}{\refreg{r_2}}$&$\stdUpdatePc{\updateHeap{\addr}{\var{w}}}$&$\memreg(r_1) = \stdcap$ and $\perm \in \{ \rwx, \rwlx, \readwrite, \readwritel\}$  and $\start \leq \addr \leq \addrend$ and $\var{w} = \memreg(r_2)$
                                                                                       and if $\var{w} = ((\_,\local),\_,\_,\_)$, then $\perm \in \{\rwlx,\readwritel \}$\\
    \hline
    \multicolumn{3}{|c|}{$\cdots$}\\
    \hline
    \_&$\failed$&otherwise\\
    \hline
  \end{tabular}
  \caption{An excerpt from the operational semantics.}
  \label{fig:op-sem}
\end{figure}

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,5) rectangle (7.6,11.5);
        \capbrace{(4.6,5)}{(4.6,12)}{sp}
      \end{scope}
    \end{tikzpicture}
    \caption{Just before we return to the adversary. Our stack frame
      is the topmost, and we do not have access to the adversary stack frame.}
  \label{fig:illu-intro}
  \end{subfigure}
\begin{subfigure}{0.033\linewidth}
  % padding
  \phantom{a}
\end{subfigure}
  \begin{subfigure}[t]{0.3\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace{(4.6,2)}{(4.6,12)}{sp}
      \end{scope}
    \end{tikzpicture}
    \caption{Just after we returned to the adversary but did not take
      care to clear our local stack frame.}
  \label{fig:illu-priv-data}
  \end{subfigure}
\begin{subfigure}{0.033\linewidth}
  % padding
  \phantom{a}
\end{subfigure}
  \begin{subfigure}[t]{0.3\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace{(4.6,2)}{(4.6,12)}{sp}
      \end{scope}
    \end{tikzpicture}
    \caption{Just after we returned to the adversary, and we did take
      care to clear our local stack frame.}
  \label{fig:illu-clear-priv}
  \end{subfigure}
  \begin{subfigure}[t]{0.33\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,7) rectangle (7.6,11.5);
        \capbrace{(4.6,7)}{(4.6,13)}{sp}
      \end{scope}
    \end{tikzpicture}
  \caption{After an adversary has called us, and we have called the adversary.}
  \label{fig:illu-call-adv}
\end{subfigure}
\begin{subfigure}[t]{0.02\linewidth}
  % padding
  \phantom{a}
\end{subfigure}
  \begin{subfigure}[t]{0.3\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace{(4.6,2)}{(4.6,13)}{sp}
      \end{scope}
    \end{tikzpicture}
  \caption{After the adversary has returned to us, and we have
    returned from the first adversary call. At this point, the adversary has
    access to the local state from the nested adversary call.}
  \label{fig:illu-adv-data}
\end{subfigure}
\begin{subfigure}[t]{0.02\linewidth}
  % padding
  \phantom{a}
\end{subfigure}
  \begin{subfigure}[t]{0.3\linewidth}
    \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

      % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbrace{(4.6,2)}{(4.6,13)}{sp}
      \end{scope}
    \end{tikzpicture}
  \caption{After the adversary has returned to us, and we have
    returned from the first adversary call after we took care to clear the
    unused part of the stack.}
  \label{fig:illu-clear-all}
  \end{subfigure}
  \caption{Depictions of the stack in relation to stack clearing.
    The greyed out areas are parts of the stack that are not accessible at the
    time.
    The sp capability is the stack pointer.}
  \label{fig:ret-adv2}
\end{figure}
\textbf{Invoking the adversary} A slightly more complex case is invoking the
adversary. As above, we clear all the non-argument registers, as well as the
part of the stack that we are not using (because, as above, it may contain local
capabilities from previously executed code that the adversary could exploit in
the same way). We leave a copy of the stack pointer in $r_\stk$, but only after
we have used the $\subseg{}{}{}$ instruction to shrink its authority to the part
that we are not using ourselves.

@@

We need the future world relation to be extensional, so we do not actually remove a revoked temporary region from the world, but we turn it into a special revoked region that exists for this purpose.
Such a revoked region contains no state transition system and puts no requirements on the memory.
It simply serves as a mask for a revoked temporary region.
Masking a region like this goes back to earlier work of \citet{Ahmed2004semantics} and was also used by \citet{Thamsborg:2011:KLR:2034773.2034831}.

@@

\begin{toplas}
  In order to be able to solve the recursive domain equation, we want the future world relations to be extensional.
  Intuitively, the future world relation specifies how memory protocols may change over time.
  If the future world relation was not extensional, then the protocols could just disappear entirely regardless of what they promise.
  A piece of memory can still be repurposed under the right circumstances, i.e., if the protocol allows it under the future world relation used.
  In practice, the extensionality of future worlds means that a future world cannot forget about region names in a past world.
  This is the reason we use masks rather than deleting the regions altogether.
  It does not, however, matter what kind of region is used as a mask; it is the region name we must retain.
  This is why we allow revoked regions to be replaced by other regions in the two future world relations.
  This may seem unnecessary as the future world relation allows new regions to be added.
  However, for technical reasons in private future worlds, we need to be able to reinstate old regions with the same region names as they had in a past world.
  Further, we do not want public future worlds to be able to prevent reinstation in private future worlds.
  Private future worlds cannot revoke permanent regions, so we cannot allow public future worlds to use permanent regions as masks for revoked regions.
\end{toplas}

@@

%subsection introduction
% \dominique{I would try to motivate the LR defs by saying that the LR is
%   constructed to express the FTLR and the FTLR says that if a piece of code only
%   has access to values respecting the invariants in a world, then it will
%   respect them itself too.} 
The logical relation defines semantically when values, program counters, and configurations are capability safe.
The logical relation is defined found in \figurename{}s~\ref{fig:logrel} and~\ref{fig:perm-conds}, and we provide some explanations in the following paragraphs.
For space reasons, we omit some definitions and explain them only verbally, but precise definitions can be found in the appendix.
The logical relation is recursively defined, so we encourage first time readers to just read the section in its entirety and do a second read afterwards.
